\documentclass[main.tex]{subfiles}

\begin{document}
\chapter{Project Management}
\chaplabel{projectManagement}
This chapter gives a high level overview of various management aspects of the project. A status update summarises the work completed to date, and provides details of the changes that have occurred since the submission of the project charter. The main stakeholders involved with the project are then identified, and their roles are explained. The division of the project workload amongst the team members is shown in the work breakdown structure, and a Gantt chart is used to organise this work over the timeline of the project. A risk assessment is performed to find and address safety risks, as well as risks to project failure. Finally, the budget for the project is presented and analysed.  
\textcolor{red}{The paragraph above is an intro to this chapter, need to check it's ok after the chapter has been completed - RK}
\section{Status Update}
\textcolor{red}{Appraise progress of project, summary of work completed, is project on track? What changes have been made since the charter (goals, specs, funding situation)?}
\section{Stakeholders}

\section{Work Breakdown Structure and Gantt Chart}
\textcolor{red}{Need to update WBS to reflect changes in project (same goes with Gantt chart)}
\section{Risk Management}
\section{Budget}
\textcolor{red}{Income and expenditure (to-date and projected), as well as in-kind funding and student hours. Is the project on track financially?}
\end{document}